### 2023-06-15 Draft.tex
Started writing Linear Filter

\section{Introduction}

>>>>

\section{Introduction}
\section{Linear Filters}
As its name suggests, the function which is used to pass the image through
must be linear and shift invariant.

A common formula for linear filtering is the \emph{Correlation Filtering}.
\[
    g(i,j) = \sum_{l \in \mathscr{M}}\sum_{k \in \mathscr{N}}{f(i+k, j+l) \cdot h(k, l)}
\]
or commonly notated as $g = f \otimes h$.\hfill\\

The desired output pixel $g(i, j)$, where $i$ and $j$ specify the
coordinates of it, is based on a $M \times N$ sized neighborhood, 
meaning not only does one pixel define an output pixel, but also a specified number
of its neighbors. The influence of each pixel in the neighborhood is defined by the filter coefficient $h(k, l)$,
also called its \emph{kernel} or \emph{mask}.\\

An interesting note is that, when the kernel is convolved with an impulse signal(an image with 0 everywhere except the origin),
it reproduces the kernel itself, whereas with correlational filtering, it produces the reflected signal.
$$
\underbrace{
    \begin{bmatrix}
        128 & 34 & 123\\
        68 & 54 & 73 \\
        100 & 95 & 17
    \end{bmatrix}}_{\text{input neighborhood}}
\otimes
\underbrace{
    \begin{bmatrix}
        0.1 & 0.1 & 0.1\\
        0.1 & 0.2 & 0.1\\
        0.1 & 0.1 & 0.1
    \end{bmatrix}}_{\text{kernel}}
= 75
$$

As the above example with a $3 \times 3$ kernel, a total of 9 pixels is needed to calculate a single output pixel.\\

Another common variant on the formula is having the signs of the offsets reversed.
\[
    g = f \ast h
\]
\[
    g(i,j) = \sum_{l \in \mathscr{M}}\sum_{k \in \mathscr{N}}{f(i-k, j-l) \cdot h(k, l)}
\]
With this formula, $\ast$ is called the \emph{convolutional} operator, and the kernel $h$ is called the \emph{impulse response function}.
